Report on Late Winter2013 Production: Image Differencing

### 2013-03-29 W13report.tex
Added Russ' section.

Compare the measured S/N of the DiaSources with the detection threshold.

@@

\begin{table}
\centering
\begin{tabular}{lcc}
\hline
\multicolumn{3}{|c|}{Theoretical Number of False Detections per Sensor} \\
\hline
Visit    & FWHM (pixels) & N\\
\hline
v6866601 & 3.0 & N \\
v6866602 & 4.4 & N \\
v6866603 & 6.0 & N \\
\end{tabular}
\caption{Total number of false detections that we expect based on
  {\bf blah}.  We list the total number of positve {\it plus} negative detections;
  they should be present in equal quantities. \label{tab-fp}
}
\end{table}

>>>>

We measured flux of {\tt DiaSources} on postfiltered difference images
using PSF--weighted flux photometry (as implemented in the LSST
measurement algorithm "flux.psf").  For measuring fluxes of point
sources on prefiltered images we implemented a new algorithm
"flux.filtered", which works as follows:
%
\[flux = \frac{\sum_{(x,y)}I(x,y) * \phi(x,y)}{\sum_{(x',y')}\phi^2(x',y')}\]
%

where $I(x,y)$ is the image before PSF filtering and $\phi(x,y)$ is an
image of the PSF centered on the source. This equation assumes an
isolated point source, an assumption that is reasonable for difference
images.  We do not weight by the per--pixel variance to avoid
non--linearity in the flux measurement, at the expense of less precise
measurements.

Filtering is performed by convolving the image with its PSF, so the
peak of the filtered image of a given source is:
%
\[Ipeak_{filt} = \sum_{(x,y)}I(x,y) * \phi(x,y)\]
%
Hence the equation for measuring its flux reduces to:
%
\[flux = \frac{Ipeak_{filt}}{\sum_{(x',y')}\phi^2(x',y')}\]
%
Similarly, the predicted uncertainty of the flux measurement is:
%
\[\sigma = \frac{\sqrt{\sum_{x,y}\sigma{^2(x,y)}\phi^2(x,y)}}{\sum_{x',y'}\phi^2(x',y')}\]
%
where $\sigma{^2(x,y)}$ is the is the per-–pixel variance of the
unfiltered image. This reduces to the following:
%
\[\sigma = \frac{\sqrt{\sigma peak{_{filt}^2}}}{\sum_{x',y'}\phi^2(x',y')}\]
%
where $\sigma peak{_{filt}^2}$ is the value of the variance plane,
after filtering, at the peak of the source.

The center of each source is determined using an LSST adaptation of
the SDSS centroiding algorithm "centroid.sdss". In general the source
will not be centered on a pixel, so "flux.filtered" uses a Lanczos 4
resampling kernel to shift the source to be centered on the nearest
pixel before applying the equations above.

@@

\begin{table}
\centering
\begin{tabular}{lcc}
\hline
\multicolumn{3}{|c|}{Theoretical Number of False Detections per Sensor} \\
\hline
Visit    & FWHM (pixels) & N\\
\hline
v6866601 & 3.0 & N \\
v6866602 & 4.4 & N \\
v6866603 & 6.0 & N \\
\end{tabular}
\caption{Total number of false detections that we expect based on
  {\bf blah}.  We list the total number of positive {\it plus} negative detections;
  they should be present in equal quantities. \label{tab-fp}
}
\end{table}
